### 2017-11-28 monograph/thesis/chapters/object_beautifier.tex
Completed the object_beautifier.tex translations to English.

\subsection{The Problem}

@@

\subsubsection{General Goals}

@@

    A vantagem nesta abordagem é não ter a necessidade de ter-se conhecimento da sintaxe das linguagens de programação
    que se irão fazer o parsing.
    Isso porque trataremos elas como texto comum,
    e será o usuário final que fará a configuração das transformações que serão aplicados no texto,
    dando liberdade de facilmente se configurar várias linguagens de programação,
    aproveitando o fato de que muitas deles compartilham estruturas semelhantes senão idênticas.

    The advantage of this approach is that we do not need to be aware of the syntax of programming languages that will
    parse.
    This is because we will treat them as common text,
    and it will be the end user that will configure the transformations that will be applied in the text,
    giving freedom to easily configure several programming languages,
    taking advantage of the fact that many of them share similar but not identical structures.

    A literatura/programas atuais são dependentes de linguagem de programação. Minha proposta é
    fazer este processo independente de linguagem, mas de dialetos como este exemplo tirado do PDF
    em anexo a este e-mail `Initial check list tasks to do.pdf':

@@

    A abordagem acima é uma abordagem ingênua, portanto somente brevemente ilustrativa. O real motor
    para o software é baseado em expressões regulares e um pilha de contextos. Esta ideia foi
    inicialmente desenvolvida pelo editor de texto `Sublime Text' \cite{Skinner}. Este editor
    utiliza essa estrutura de blocos para fazer a sintaxe highlighting do códigos das linguagens
    através de expressões regulares alocação de contextos/escopos. Essa mesma abordagem pode ser
    utilizada pelo usuário para definir em quais regiões uma Máquina de Turing (linguagens C++/Rust)
    devem fazer/propor as alterações no código.

\subsubsection{Ideas}

    Os pontos positivos dessa abordagem para um formatador de código são a reusabilidade de
    componentes entre as linguagens pelo usuário final da aplicação ao invés do programador, o que
    torna este software muito mais genérico e abre a possibilidades de maior sucesso para a criação
    definitiva de um formatador Universal de códigos das linguagens de programação, quaisquer sejam
    elas. Por exemplo, `if/for/while'\textquotesingle s em linguagens de programação como C++ e Java
    são da mesma estrutura. Assim temos que escrever somente uma vez a especificação para um
    componente da linguagem sem recorrer a programação de do código do programa. Isso tem a vantagem
    de por der ser configurado pelo usuário final ao invés do programador, assim fica mais simples
    de configurar e expandir o conjunto de linguagens disponíveis ao processamento/beautifying.

    Ideas for implementation:

@@

\subsubsection{Listings}

    Algumas bibliotecas existentes, e potencialmente utilizadas como `syntect` para o auxílio na
    construção do produto de software:

@@

    Segue-se uma lista básica de formatters/beautifiers acessado no endereço
    \lword{\url{http://www.softpanorama.org/Utilities/beautifiers.shtml}} em março/2017:

@@

\subsubsection{Related Works}

    Após a busca do que há de publicações científicas sobre o assunto e entra-se alguns trabalhos na
    área específica e similar aos trabalhos feitos pelor formatadores de códigos (Beautifiers).
    Nessa modalidade de trabalho, pode-se confundir-se com artigos que tratam sobre o `Prettyprint`,
    que trata-se de colorir o texto e exibir-lo ao usuário. O que não é o que se busca nesse
    trabalho, mas sim fazer alterações no texto sobre a forma como ele é estruturado, apresentado ao
    usuário e salvo em disco. Seguem as seguintes publicações:

@@

\subsubsection{Obfuscators}

    Aqui encontra-se o lado oposto dessas ferramentas, Source Code Obfuscators, que servem para
    destruir o visual do código. Usualmente utilizado para dificultar a leitura por outras pessoas
    ou ainda reduzir o tamanho de códigos de linguagens scripting que devem ser carregadas/baixadas
    por navegadores de internet, assim diminuindo o tráfego de internet e salvando/economizando
    largura de banda para download:

\subsubsection{Future Works}

>>>>

\section{The Problem}

@@

\subsection{General Goals}

@@

    This proposed work approach has the advantage of do not previously require we, this tools developers,
    to be aware of the of programming languages syntaxes which will be parsed by its users.
    This come from the fact that we will treat everything just as common plain text,
    and end user will be hold responsible to correctly configure the formatting transformations to be applied into the
    text or source code.
    As so,
    giving freedom to easily configure several programming languages,
    taking advantage of the fact that many of them share similar but not identical structures.
    TODO,
    put reference to this.

    Existing `Beautifiers' program\s are programming language dependent.
    This proposal is to make this process independent of language,
    but of dialects like this example:

@@

    In short,
    the above approach is only briefly illustrative,
    as the software engine is based on regular expressions and a stack of contexts.
    This idea to be empowered was initially developed by the text editor `Sublime Text' \cite{Skinner}.
    The `Sublime Text' editor uses such block structures to do the syntax highlighting of its source code languages.
    The idea here is to use the same approach,
    so the end user can define in which regions the `Object Beautifier' should propose, i.e.,
    perform changes to the code.
    Currently this would be equivalent to the same way `Sublime Text' users\q create their own syntaxes highlighting.
    TODO,
    put a reference to this.

    The strengths of this approach to a code formatter are the reusability of components between languages by the end
    user of the application rather than the beautifier programmer,
    which makes this software much more generic and opens the possibilities of greater success for the definitive
    creation of a Universal Code formatter for programming languages and even plain text files.
    For example,
    `if/for/while'\q in programming languages like `C++' and `Java' have the same syntax structuring,
    so we have to write only once the specification for a language component like `if/for/while'\q.
    This has the advantage of being configured by the end user rather than the programmer,
    hence it is simpler to configure and expand the set of languages available for beautifying.

\subsection{Obfuscators}

    Here you will find the opposite side of Source Code Beautifiers.
    Source Code Obfuscators,
    is useful to destroy the formatting of the code.
    Often used to make it difficult for other people to read or to reduce the size of scripting languages that should be
    uploaded/downloaded by internet browsers,
    thus reducing internet traffic and saving download bandwidth:

\section{Future Works}

\chapter{Draft for implementation}

    This chapter will not be presented on the monograph definitive version.
    It only is a collection of articles,
    tools and websites which should be considered useful for this work, i.e., ideas and references.

@@

    Some existing libraries,
    and to be potentially used as `syntect` for assistance in building the software product:

@@

    The following is a basic list of formatters/beautifiers accessed at
    \lword{\url{http://www.softpanorama.org/Utilities/beautifiers.shtml}} on march/2017:

@@

\section{Related Programs for Beautifying}

    After the search of the scientific publications on the subject,
    it was found some works in the specific area similar to the works done by code formatters (Beautifiers).
    However,
    source code beautifying is ambiguous definition which can be easily confused with `Prettyprinting',
    which is about coloring the text and displaying it to the user.
    `Prettyprint' is not is sought in this work implementation,
    but rather make changes in the text on how it is structured,
    presented to the user and saved on the file system.

    Following we may find some references and publications for source code beautifying,
    which should be used futurely by this monograph study:

@@
